Response to reviewers

### 2022-06-07 paper/paper-jsdse/paper-jsdse.tex
clarified the 84 hours per week

\begin{itemize}
\tightlist
\item
  If the hourly rate is recorded as 0, we set wage as missing, and
\item
  If the total hours of worked per week for the corresponding job is greater than 84 hours, we set the wage and hours worked as missing.
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  If the hourly rate is recorded as 0, we set wage as missing, and
\item
  If the total hours of worked per week for the corresponding job is greater than 84 hours (12 hours/day every day), we set the wage and hours worked as missing.
\end{itemize}

### 2022-06-07 paper/paper.Rmd
clarified the 84 hours per week

* If the hourly rate is recorded as 0, we set wage as missing, and
* If the total hours of worked per week for the corresponding job is greater than 84 hours, we set the wage and hours worked as missing.

>>>>

* If the hourly rate is recorded as 0, we set wage as missing, and
* If the total hours of worked per week for the corresponding job is greater than 84 hours (12 hours/day every day), we set the wage and hours worked as missing.

### 2022-06-07 response/response3.Rmd
clarified the 84 hours per week

* Corrected as follows.

@@

* The abstract does NOT promise an exploratory analysis for longitudinal data. It mentions that one of the purposes of this textbook data is to use it to teach exploratory analysis of longitudinal data. Similarly, it also states that the data is useful for teaching modeling. Both of these are beyond the scope of this paper. They are still important to keep because it makes the reader aware of why this data is useful and important. No change to abstract was made.

@@

* It is assumed that people usually do not work more than 12 hours a day. Moreover, this value is more than the cut-off of upper value if we used the IQR method, which is only 67 hours.

>>>>

* Corrected as detailed below.

@@

* The abstract does NOT promise an exploratory analysis for longitudinal data. It mentions that one of the purposes of this textbook data is to use it to teach exploratory analysis of longitudinal data. Similarly, it also states that the data is useful for teaching modeling. Both of these are beyond the scope of this paper. The mention is still important to keep because it makes the reader aware of why this data are useful and important for education. No change to abstract was made.

@@

* This corresponds to 12 hours per day, each day of the week, which is a reasonable upper limit on the expectation of the maximum amount of hours worked per week. It is quite a high upper bound, and higher than the IQR of 67. We have added clarification in the text.
